MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives

### 2017-09-19 ArticleRevision/article_with_markings/letter/letter.tex
Finished shortening sections 1, 2, & 3. Still need to emphasize the bag-representative selector for reviewer 2

@@

@@

@@

@@

\noindent Thank you for pointing out that statement. What we meant was that they assume that all the instances within positive bags are assumed to be positive, or to follow the distribution of positively labelled data.

@@

\noindent We apologize for the ambiguity. What we were specifying was the MIRSVM bag-representative selector and formutlation. We've made the appropriate change in text.

@@

@@

>>>>

\noindent We tried to be as thorough as possible during our experimental study and we intend on continuing with this method of experimentation. We really appreciate your comment on this.

@@

\noindent We made some changes to sections 1, 2, and 3 to try and condense the information given. We shortened and rewrote some of the descriptions on the background of multiple-instance learning, as well as removed some of the basic SVM formulations from the SVM background to avoid repetition in Section 3. Your comment on the length of those sections makes sense and we hope to made the information more concise.

@@

\noindent Thank you for noting this. As you've suggested, we added a couple of additional applications of the standard MI assumption to the paper. We hope that the following real-world scenarios provide a more global picture as to why MI algorithms are useful.
\begin{enumerate}
\item Bioinformatics: Protein Identification
\item Image classification \& retrieval
\item Web mining \& text classification
\item Medical diagnosis \& imaging
\end{enumerate}

@@

\noindent According to your suggestion, we tested the performance of our method using a wider range of parameters (especially with lower C values). Results were exactly the same as originally reported, since the best parameters were still selected in the domain we originally defined. The only difference of evaluating a larger number of parameters would be a longer runtime, but we observed no performance different in the results for any of the datasets evaluated. Thank you.

@@

\noindent Thank you for pointing out that statement. What we meant was that they assume that all the instances within positive bags are assumed to be positive, or to follow the distribution of positively labelled data. This statement was clarified in the text. Please let us know if it needs any further explanation.

@@

\noindent We apologize for the ambiguity. What we were specifying was the MIRSVM bag-representative selector and formutlation, referenced by Equations 12 and 13. We've made the appropriate change in text to clarify the thought.

@@

\noindent We've updated the text to the correct grammar. Thanks for pointing that out.

@@

\noindent Yep that's correct, thanks for catching that! We've updated the text to be ``Gram matrix".
